\\textsc{Mathematical Description}

### 2023-06-08 100-math-description/GR-sslcm-math-description.Rmd
Improve rendering to .docx

@@

$\rho_{\pi_{i=\fall,j,j^{\prime}}}$

@@

@@

```{r index-table}
# read in csv version of table
tab = read.csv("01-indices.csv", allowEscapes = TRUE)

@@

# build the table
kable(tab[,1:3], "latex", booktabs = TRUE, linesep = "", caption = index_tab_cap, escape = FALSE) %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD")) %>%
  row_spec(0, bold = TRUE) %>%
  column_spec(1, width = "50px") %>%
  column_spec(2, width = "50px") %>%
  column_spec(3, width = "332px") %>%
  collapse_rows(1, valign = "bottom", latex_hline = "major") %>%
  footnote(number = footnote_key, threeparttable = TRUE, escape = FALSE)
```

@@

```{r symbol-table}
tab = read.csv("02-symbols.csv", allowEscapes = TRUE)

@@

handle_eqs = function(x) {
  if (x == "") {
    out = ""
  } else {
    x_split = unlist(stringr::str_split(x, ","))
    x_split = stringr::str_remove_all(x_split, " ")
    x_refs = paste0("\\ref{eq:", x_split, "}")
    out = paste(x_refs, collapse = ", ")
  }
  return(out)
}

@@

kable(tab[,2:5], "latex", booktabs = TRUE, linesep = "", caption = symbol_tab_cap, escape = FALSE, longtable = TRUE) %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD", "repeat_header")
                # repeat_header_continued = "\\textit{(Continued on next page...)}"
                ) %>%
  row_spec(0, bold = TRUE) %>%
  pack_rows("Freshwater Juvenile", min(which(tab$Phase == 1)), max(which(tab$Phase == 1)), bold = TRUE, hline_after = TRUE) %>%
  pack_rows("Ocean Juvenile", min(which(tab$Phase == 2)), max(which(tab$Phase == 2)), bold = TRUE, hline_after = TRUE) %>%
  pack_rows("Freshwater Adult", min(which(tab$Phase == 3)), max(which(tab$Phase == 3)), bold = TRUE, hline_after = TRUE) %>%
  column_spec(1, width = "25px") %>%
  column_spec(2, width = "50px") %>%
  column_spec(3, width = "50px") %>%
  column_spec(4, width = "300px") %>%
  collapse_rows(1, valign = "bottom", latex_hline = "full")
```

@@

```{r param-table}
tab = read.csv("03-params.csv", allowEscapes = TRUE)

@@

footnote_key = c(
  "1" = "Beta Distribution: $b(\\\\mathrm{shape}_1$, $\\\\mathrm{shape}_2)$",
  "2" = "Normal Distribution: $\\\\mathcal{N}(\\\\mathrm{mean}$, $\\\\mathrm{precision})$",
  "3" = "Uniform Distribution: $\\\\mathcal{U}(\\\\mathrm{lower}$, $\\\\mathrm{upper})$",
  "4" = "$t$-Distribution: $t$(mean, precision, degrees of freedom); this prior results in approximately a $\\\\mathcal{U}(0,1)$ prior after inverse-logit transformation \\\\citep{dorazio-etal-2011}.",
  "5" = "Dirichlet Distribution: $\\\\mathcal{D}(\\\\mathrm{shape}_1$, $\\\\mathrm{shape}_2$, $\\\\mathrm{shape}_3)$",
  "6" = "Scaled Inverse-Wishart Distribution: $\\\\mathcal{SIW}$(\\\\textbf{S}, degrees of freedom); \\\\textbf{S} is a vector of scale parameters for scaled-Wishart; see JAGS v4.3.0 user manual page 62 for details on this prior. Briefly, the scale parameters of 0.10 - 0.30 places higher prior weight on small values of the the component $\\\\sigma$ parameters, which was intentional because these represent variability on the log- or logit-scale. Setting the degrees of freedom to 2 results in a $\\\\mathcal{U}(-1,1)$ prior on the $\\\\rho$ components."
)

@@

kable(tab[,2:5], "latex", booktabs = TRUE, linesep = "", caption = param_tab_cap, escape = FALSE, longtable = TRUE) %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD", "repeat_header")
                # repeat_header_continued = "\\textit{(Continued on next page...)}"
                ) %>%
  row_spec(0, bold = TRUE) %>%
  pack_rows("Freshwater Juvenile", min(which(tab$Phase == 1)), max(which(tab$Phase == 1)), bold = TRUE, hline_after = TRUE) %>%
  pack_rows("Ocean Juvenile", min(which(tab$Phase == 2)), max(which(tab$Phase == 2)), bold = TRUE, hline_after = TRUE) %>%
  pack_rows("Freshwater Adult", min(which(tab$Phase == 3)), max(which(tab$Phase == 3)), bold = TRUE, hline_after = TRUE) %>%
  column_spec(1, width = "50px") %>%
  column_spec(2, width = "65px") %>%
  column_spec(3, width = "20px") %>%
  column_spec(4, width = "290px") %>%
  row_spec(1:(nrow(tab)-1), hline_after = TRUE) %>%
  footnote(number = footnote_key, number_title = "Prior Distributions:", title_format = c("italic", "underline"), escape = FALSE, threeparttable = TRUE)
```

@@

```{r data-table}
tab = read.csv("04-data.csv", allowEscapes = TRUE)

@@

kable(tab[,2:5], "latex", booktabs = TRUE, linesep = "", caption = data_tab_cap, escape = FALSE, longtable = TRUE) %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD", "repeat_header")
                # repeat_header_continued = "\\textit{(Continued on next page...)}"
                ) %>%
  row_spec(0, bold = TRUE) %>%
  pack_rows("Freshwater Juvenile", min(which(tab$Phase == 1)), max(which(tab$Phase == 1)), bold = TRUE, hline_after = TRUE) %>%
  pack_rows("Freshwater Adult", min(which(tab$Phase == 3)), max(which(tab$Phase == 3)), bold = TRUE, hline_after = TRUE) %>%
  column_spec(1, width = "50px") %>%
  column_spec(2, width = "70px") %>%
  column_spec(3, width = "20px") %>%
  column_spec(4, width = "295px") %>%
  collapse_rows(1, valign = "bottom", latex_hline = "full")
```

@@

```{r equation-table}
tab = read.csv("05-equations.csv", allowEscapes = TRUE)

@@

kable(tab[,2:4], "latex", booktabs = TRUE, linesep = "", caption = equation_tab_cap, escape = FALSE, longtable = TRUE, align = "lrl") %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD", "repeat_header")
                # repeat_header_continued = "\\textit{(Continued on next page...)}"
                ) %>%
  row_spec(0, bold = TRUE) %>%
  pack_rows("Generic", min(which(tab$Phase == 0)), max(which(tab$Phase == 0)), bold = TRUE, hline_after = TRUE) %>%
  pack_rows("Freshwater Juvenile", min(which(tab$Phase == 1)), max(which(tab$Phase == 1)), bold = TRUE, hline_after = TRUE) %>%
  pack_rows("Ocean Juvenile", min(which(tab$Phase == 2)), max(which(tab$Phase == 2)), bold = TRUE, hline_after = TRUE) %>%
  pack_rows("Freshwater Adult", min(which(tab$Phase == 3)), max(which(tab$Phase == 3)), bold = TRUE, hline_after = TRUE) %>%
  column_spec(1, width = "55px") %>%
  column_spec(2, width = "15px") %>%
  column_spec(3, width = "365px") %>%
  collapse_rows(1, valign = "bottom", latex_hline = "major")
```

@@

```{r year-table}

@@

kable(tab, "latex", booktabs = TRUE, align = "cccc", linesep = "", col.names = c("Return Year", "Age-3", "Age-4", "Age-5"), escape = FALSE,
      caption = year_tab_caption, row.names = FALSE) %>%
  kable_styling(full_width = FALSE) %>%
  add_header_above(c(" " = 1, "Brood Year of Returning Adults by Age" = 3), bold = TRUE) %>%
  row_spec(0, bold = TRUE) %>%
  column_spec(1, bold = TRUE) %>%
  column_spec(2:4, width = "50px")
```

>>>>

```{r my-kable-fn}
my_kable = function(x, ...) {

  # detect the kable format
  kable_format = ifelse(is_latex_output(), "latex", "markdown")

  # build the kable with supplied options as well as my fixed defaults
  kable(x = x, format = kable_format, escape = FALSE, booktabs = TRUE, linesep = "", ...)
}
```

@@

@@

\newpage

@@

```{r index-table, warning = FALSE}
# read in csv version of table
tab = read.csv("01-indices.csv", allowEscapes = TRUE)

@@

# build the table
my_kable(x = tab[,1:3], caption = index_tab_cap) %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD")) %>%
  row_spec(0, bold = TRUE) %>%
  column_spec(1, width = "50px") %>%
  column_spec(2, width = "50px") %>%
  column_spec(3, width = "332px") %>%
  collapse_rows(1, valign = "bottom", latex_hline = "major") %>%
  footnote(number = footnote_key, threeparttable = TRUE, escape = FALSE)
```

\newpage

@@

```{r symbol-table, warning = FALSE}
tab = read.csv("02-symbols.csv", allowEscapes = TRUE)

@@

handle_eqs = function(x) {
  if (x == "") {
    out = ""
  } else {
    x_split = unlist(stringr::str_split(x, ","))
    x_split = stringr::str_remove_all(x_split, " ")
    if (is_latex_output()) {
      x_refs = paste0("\\ref{eq:", x_split, "}")
    } else {
      x_refs = paste0("\\@ref(eq:", x_split, ")")
    }
    out = paste(x_refs, collapse = ", ")
  }
  return(out)
}

@@

my_kable(x = tab[,2:5], caption = symbol_tab_cap, longtable = TRUE) %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD", "repeat_header")
                # repeat_header_continued = "\\textit{(Continued on next page...)}"
                ) %>%
  row_spec(0, bold = TRUE) %>%
  pack_rows("Freshwater Juvenile", min(which(tab$Phase == 1)), max(which(tab$Phase == 1)), bold = TRUE, hline_after = TRUE) %>%
  pack_rows("Ocean Juvenile", min(which(tab$Phase == 2)), max(which(tab$Phase == 2)), bold = TRUE, hline_after = TRUE) %>%
  pack_rows("Freshwater Adult", min(which(tab$Phase == 3)), max(which(tab$Phase == 3)), bold = TRUE, hline_after = TRUE) %>%
  column_spec(1, width = "25px") %>%
  column_spec(2, width = "50px") %>%
  column_spec(3, width = "50px") %>%
  column_spec(4, width = "300px") %>%
  collapse_rows(1, valign = "bottom", latex_hline = "full")
```

\newpage

@@

```{r param-table, warning = FALSE}
tab = read.csv("03-params.csv", allowEscapes = TRUE)

@@

footnote_key = c(
  "1" = "Beta Distribution: $b(\\\\mathrm{shape}_1$, $\\\\mathrm{shape}_2)$",
  "2" = "Normal Distribution: $\\\\mathcal{N}(\\\\mathrm{mean}$, $\\\\mathrm{precision})$",
  "3" = "Uniform Distribution: $\\\\mathcal{U}(\\\\mathrm{lower}$, $\\\\mathrm{upper})$",
  "4" = "$t$-Distribution: $t$(mean, precision, degrees of freedom); this prior results in approximately a $\\\\mathcal{U}(0,1)$ prior after inverse-logit transformation \\\\citep{dorazio-etal-2011}.",
  "5" = "Dirichlet Distribution: $\\\\mathcal{D}(\\\\mathrm{shape}_1$, $\\\\mathrm{shape}_2$, $\\\\mathrm{shape}_3)$",
  "6" = "Scaled Inverse-Wishart Distribution: $\\\\mathcal{SIW}$(\\\\textbf{S}, degrees of freedom); \\\\textbf{S} is a vector of scale parameters for scaled-Wishart; see JAGS v4.3.0 user manual page 62 for details on this prior. Briefly, the scale parameters of 0.10 - 0.30 places higher prior weight on small values of the component $\\\\sigma$ parameters, which was intentional because these represent variability on the log- or logit-scale. Setting the degrees of freedom to 2 results in a $\\\\mathcal{U}(-1,1)$ prior on the $\\\\rho$ components."
)

@@

my_kable(x = tab[,2:5], caption = param_tab_cap, longtable = TRUE) %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD", "repeat_header")
                # repeat_header_continued = "\\textit{(Continued on next page...)}"
                ) %>%
  row_spec(0, bold = TRUE) %>%
  pack_rows("Freshwater Juvenile", min(which(tab$Phase == 1)), max(which(tab$Phase == 1)), bold = TRUE, hline_after = TRUE) %>%
  pack_rows("Ocean Juvenile", min(which(tab$Phase == 2)), max(which(tab$Phase == 2)), bold = TRUE, hline_after = TRUE) %>%
  pack_rows("Freshwater Adult", min(which(tab$Phase == 3)), max(which(tab$Phase == 3)), bold = TRUE, hline_after = TRUE) %>%
  column_spec(1, width = "50px") %>%
  column_spec(2, width = "65px") %>%
  column_spec(3, width = "20px") %>%
  column_spec(4, width = "290px") %>%
  row_spec(1:(nrow(tab)-1), hline_after = TRUE) %>%
  footnote(number = footnote_key, number_title = "Prior Distributions:", title_format = c("italic", "underline"), escape = FALSE, threeparttable = TRUE)
```

\newpage

@@

```{r data-table, warning = FALSE}
tab = read.csv("04-data.csv", allowEscapes = TRUE)

@@

my_kable(x = tab[,2:5], caption = data_tab_cap, longtable = TRUE) %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD", "repeat_header")
                # repeat_header_continued = "\\textit{(Continued on next page...)}"
                ) %>%
  row_spec(0, bold = TRUE) %>%
  pack_rows("Freshwater Juvenile", min(which(tab$Phase == 1)), max(which(tab$Phase == 1)), bold = TRUE, hline_after = TRUE) %>%
  pack_rows("Freshwater Adult", min(which(tab$Phase == 3)), max(which(tab$Phase == 3)), bold = TRUE, hline_after = TRUE) %>%
  column_spec(1, width = "50px") %>%
  column_spec(2, width = "70px") %>%
  column_spec(3, width = "20px") %>%
  column_spec(4, width = "295px") %>%
  collapse_rows(1, valign = "bottom", latex_hline = "full")
```

\newpage

@@

```{r equation-table, warning = FALSE}
tab = read.csv("05-equations.csv", allowEscapes = TRUE)

@@

my_kable(x = tab[,2:4], caption = equation_tab_cap, longtable = TRUE, align = "lrl") %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD", "repeat_header")
                # repeat_header_continued = "\\textit{(Continued on next page...)}"
                ) %>%
  row_spec(0, bold = TRUE) %>%
  pack_rows("Generic", min(which(tab$Phase == 0)), max(which(tab$Phase == 0)), bold = TRUE, hline_after = TRUE) %>%
  pack_rows("Freshwater Juvenile", min(which(tab$Phase == 1)), max(which(tab$Phase == 1)), bold = TRUE, hline_after = TRUE) %>%
  pack_rows("Ocean Juvenile", min(which(tab$Phase == 2)), max(which(tab$Phase == 2)), bold = TRUE, hline_after = TRUE) %>%
  pack_rows("Freshwater Adult", min(which(tab$Phase == 3)), max(which(tab$Phase == 3)), bold = TRUE, hline_after = TRUE) %>%
  column_spec(1, width = "55px") %>%
  column_spec(2, width = "15px") %>%
  column_spec(3, width = "365px") %>%
  collapse_rows(1, valign = "bottom", latex_hline = "major")
```

\newpage

@@

```{r year-table, warning = FALSE}

@@

my_kable(x = tab, align = "cccc", col.names = c("Return Year", "Age-3", "Age-4", "Age-5"), 
         caption = year_tab_caption, row.names = FALSE) %>%
  kable_styling(full_width = FALSE) %>%
  add_header_above(c(" " = 1, "Brood Year of Returning Adults by Age" = 3), bold = TRUE) %>%
  row_spec(0, bold = TRUE) %>%
  column_spec(1, bold = TRUE) %>%
  column_spec(2:4, width = "50px")
```

\newpage
